Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-18 paper/paper.tex
Include query coordinates in the report
Include the date that the geodata was collected

For the purpose of this project, the OpenStreetMap road dataset has been used in the presentation of the road network around Stockholm, and in the generative process of new road networks. To assess and correct path widths and path node locations, the OpenStreetMap building footprint dataset has also been used. To make an assessment on the quality and precision of the OpenStreetMap data, the SLU map from the Swedish National Land Survey was used in comparison with the OpenStreetMap map. The SLU map conatins only building footprints and property limits. Both map segments were obtained around the Stockholm greater metropolitan area. The exact map segments that were extracted were in both cases rectangles with the following coordinates:. TODO: Get coordinates

>>>>

For the purpose of this project, the OpenStreetMap road dataset has been used in the presentation of the road network around Stockholm, and in the generative process of new road networks. To assess and correct path widths and path node locations, the OpenStreetMap building footprint dataset has also been used. To make an assessment on the quality and precision of the OpenStreetMap data, the SLU map from the Swedish National Land Survey was used in comparison with the OpenStreetMap map. The SLU map conatins only building footprints and property limits. Both map segments were obtained around the Stockholm greater metropolitan area.
The exact map segments that were extracted were in both cases rectangles with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.
